Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-04-02 2016-Weak-FH-Bisim/WeakBisim.tex
proof of lemma 6...

\begin{lemma}[Weak open transition composition]\label{lem-compose} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
	Suppose $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$ and additionally:\\[-2ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\gamma_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}\\
\text{~~and for all $p\in[0..n]$~~}
Q\models{\openrule
	{
		\gamma_{p j}^{j\in J_p},
		 \Pred_p,  
		\Post_p}
	{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
		\ostate{s_{(p+1) i}^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Let 
\begin{mathpar}
J_Q=\displaystyle{\bigcup_{p=0}^nJ_{p}}
\qquad
\Pred\,'=\Pred\land \bigwedge_{p=0}^{n}(\alpha_p=\beta_p\land \Pred_p)\bigotimes_{i=0}^{p-1}\Post_i
\\
\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}}\text{\quad and\quad}
\Post\,'=\Post\uplus\bigotimes_{p=0}^{n}
		\Post_p 
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred\,',  \Post\,'
			 }
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}
\TODO{Proof}

@@

Note: If $(\beta^i_p)_{j_0}=\tau$ Because of Definition 11, $P$ necessarily do a $\tau$ open transition and remains in the same state, ($s_p = s_{p+1}$). Thus without loss of generality, we can bypass such an open transition and obtain another decomposition of the WOT without the open transition that requires $({\beta^i_p})_{j_0}=\tau$. We can thus  suppose that for all $p$ and $i$ we have $({\beta^i_p})_{j_0}\neq\tau$.

Moreover, we have for all $p\in[0..n]$:
\begin{mathpar}
Q\models{\openrule
	{
		\gamma_{p j}^{j\in J_p},
		 \Pred_p,  
		\Post_p}
	{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
		\ostate{s_{(p+1) i}^{\, i\in L_Q}}}
}		
\end{mathpar}
In the same way,  by Lemma \ref{lem-rel-OT-WOT} we can decompose $\WOT_p$ into  a series of $m'+n'$ tau open transitions and a single observable open transition:
\[Q\models{\openrule
			{
				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred'^{2}}},  
				{{\Post'^{2}}}}
				{\ostate{s_{i}^{i\in L_Q}} \OTarrow {\alpha_p}
				\ostate{s_{i}'^{i\in L_Q}}}
				}%\]
\]
We can apply Lemma \ref{lem-compose} on each   $\symb{OT}_p$ of $P$ in the form: 
$P\!\models		
\openrule
    {
       {(\beta^i_p)^{p\in J}},\Pred_p,\Post_p   }
         {\ostate{s^{i\in L}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L}_{(p+1)i}}}$

>>>>

\begin{lemma}[Weak open transition composition]\label{lem-Weakcompose} Suppose that we have a weak open automaton such that the WOTs cannot observe silent actions (see Definition \ref{def:Non-ObsTau}).
	Suppose $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$ and additionally:\\[-2ex]
\begin{mathpar}
%\[
P\models{\openrule
	{
		\gamma_j^{j\in J}, 
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTWeakarrow {\alpha}
		\ostate{s_i'^{\, i\in L}}}
}\\
\text{~~and for all $p\in[0..n]$~~}
Q\models{\openrule
	{
		\gamma_{p j}^{j\in J_p},
		 \Pred_p,  
		\Post_p}
	{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
		\ostate{s_{(p+1) i}^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Let 
\begin{mathpar}
J_Q=\displaystyle{\bigcup_{p=0}^nJ_{p}}
\qquad
\Pred\,'=\Pred\land \bigwedge_{p=0}^{n}(\alpha_p=\beta_p\land \Pred_p)\bigotimes_{i=0}^{p-1}\Post_i
\\
\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}}\text{\quad and\quad}
\Post\,'=\Post\uplus\bigotimes_{p=0}^{n}
		\Post_p 
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\gamma_j^{j\in (J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred\,',  \Post\,'
			 }
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTWeakarrow {\alpha}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}
\TODO{Proof starts from here}

@@

Note that if $(\beta^i_p)_{j_0}=\tau$ because of Definition \ref{def:Non-ObsTau}, $P$ necessarily makes a $\tau$ open transition and remains in the same state, ($s_p = s_{p+1}$). Thus without loss of generality, we can bypass such an open transition and obtain another decomposition of the WOT without the open transition that requires ${\beta^i_{p{j_0}}}=\tau$. We can thus  suppose that for all $p$ and $i$ we have ${\beta^i_{p{j_0}}}\neq\tau$.

Moreover, we have for all $p\in[0..n]$:
\begin{mathpar}
Q\models{\openrule
	{
		\gamma_{p j}^{j\in J_p},
		 \Pred_p,  
		\Post_p}
	{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
		\ostate{s_{(p+1) i}^{\, i\in L_Q}}}
}		
\end{mathpar}
In the same way,  by Lemma \ref{lem-rel-OT-WOT} we can decompose $\WOT_p$ into  a series of $m'+n'$ tau open transitions and a single observable open transition:
\[Q\models{\openrule
			{
				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred'^{2}}},  
				{{\Post'^{2}}}}
				{\ostate{s_{i}^{i\in L_Q}} \OTarrow {\alpha_p}
				\ostate{s_{i}'^{i\in L_Q}}}
				}%\]
\]
We can apply Lemma \ref{lem-compose} on each   $\symb{OT}_p$ of $P$ in the form: 
$P\!\models		
\openrule
    {
       {(\beta^i_p)^{p\in J}},\Pred_p,\Post_p   }
         {\ostate{s^{i\in L}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L}_{(p+1)i}}}$ 
At the beginning $Q$ is at state $\ostate{s_{q0}}$. We proceed by iteration over the list  $\gamma_{j_0}=[\beta_0..\beta_n]$.\\
For each step when $P$ moves, we have two cases:
\begin{itemize}
\item If $j_0\in J$ then Q moves by one open transition, and by hypothesis  $\beta^i_{j_0}=\beta_t$ with $\beta^i_{j_0}\neq \tau$ for some $t$ such that $t$ has value $0$ at beginning and that is incremented whenever this condition is satisfied. In this case, we have:
\[Q\models{\openrule
	{
		\gamma_{t j}^{j\in J_t},
		 \Pred_t,  
		\Post_t}
	{\ostate{s_{t i}^{i\in L_Q}} \OTWeakarrow {\alpha_t}
		\ostate{s_{(t+1) i}^{\, i\in L_Q}}}
}
\]
By  Lemma \ref{lem-rel-OT-WOT} we can decompose $\WOT_t$ into  a series of $k+k'$ tau open transitions and the observable open transition:

\[Q\models{\openrule
	{
		\gamma_{t j}^{j\in J_t},
		 \Pred_t,  
		\Post_t}
	{\ostate{s_{t i}^{i\in L_Q}} \OTarrow {\alpha_t}
		\ostate{s_{(t+1) i}^{\, i\in L_Q}}}
}
\]
\begin{enumerate}

\item For the first $k$ open tau transitions, by Definition \ref{def:Non-ObsTau} $P$ can make a tau open transition and the hole makes also tau action. So by Lemma \ref{lem-compose} we obtain $k$ open transitions in the form: 
\[P[Q]_{j_0}\!\models		
\openrule
    {
       \beta_p^{(p\in J\setminus\{j_0\}) \uplus J_Q},{\Pred_p},{\Post_p}   }
         {\ostate{s^{i\in L \uplus L_Q}_{pi}} \OTarrow {\tau} \ostate{s^{i\in L\uplus L_Q }_{(p+1)i}}}\]

\item We proceed in the same way for $k'$ last weak open transitions, and we obtain $k'$ open tau transitions.\\
\item For the observable open transition. We have $\alpha_t=\beta_{j_0}$  by Lemma \ref{lem-compose} we obtain:\\ 
\[P[Q]_{j_0}\!\models		
\openrule
    {
       \beta_p^{(p\in J\setminus\{j_0\}) \uplus J_Q},{\Pred_p}\!\!'',{\Post_p}\!\!''   }
         {\ostate{s^{i\in L \uplus L_Q}_{pi}} \OTarrow {\alpha} \ostate{s^{i\in L\uplus L_Q }_{(p+1)i}}}\] \\
 such that  ${\Pred_p}\!\!'' \iff {\Pred_p}
		\land {\Pred_p}\!\!'\land \alpha_t=\beta_{j_0}$, ${\Post_p}\!\!''={\Post_p}\uplus 
		{\Post_p}\!\!'$\\ 
\end{enumerate}

By Lemma \ref{lem-rel-OT-WOT} from cases $(1)$, $2$ and $(3)$ we obtain: 
\[P[Q]_{j_0}\!\models		
\openrule
    {
       \beta_p^{(p\in J\setminus\{j_0\}) \uplus J_Q}, {\Pred_p}
		\land {\Pred_p}\!\!'\land \alpha_p'=\beta_{j_0}$, ${\Post_p}\!\!''={\Post_p}\uplus 
		{\Post_p}\!\!'}
         {\ostate{s^{i\in L\uplus L_Q}_{pi}} \OTWeakarrow {\alpha} \ostate{s^{i\in L \uplus L_Q}_{(p+1)i}}}\]

 \item Else, $j_0\not\in J$. $t$ does not move  and $Q$ does not move, i.e. we have: $\ostate{(s_{ti})^{i\in L_Q}} = \ostate{({s}_{(t+1)i})^{i\in L_Q}}$....
\end{itemize}

---------------------------------------------------------
